An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-11-18 EconGrowth2.Rnw
Added graphs of sigma vs. sigma_1 to the paper.

We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
for the CES model, based on values of $\delta$ and $\delta_1$.
The following table shows the permuted equations for each CES nesting.

@@

Figure~\ref{fig:CESq_ternary_graph_kl} shows 
$\alpha$, $\beta$, and $\gamma$ parameters from the CES model without energy.

<<CESq_ternary_graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (without energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values.">>=
cesResampleTrianglePlot(energyType=NA)
@

@@

@@

>>>>

We can develop pseudo $\alpha$, $\beta$, and $\gamma$ parameters 
for the CES model, based on values of $\delta$ and $\delta_1$.
Table~\ref{tab:CES_abg_equations} shows the permuted equations for each CES nesting.

@@

**** Replace Figures~\ref{fig:CES_ternary_graph_kl}--\ref{fig:CESq_ternary_graph_ekl}
with one plot that shows all 4 nestings. ****

Figure~\ref{fig:CES_ternary_graph_kl} shows 
$\alpha$, $\beta$, and $\gamma$ parameters from the CES model without energy.

<<CES_ternary_graph_kl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (without energy) resample model $\\alpha$, $\\beta$, and $\\gamma$ values.">>=
cesResampleTrianglePlot(energyType=NA)
@

@@

**** Fix $x$-axis on Figures~\ref{fig:CESq_Sigma_Sigma_1_kle}--\ref{fig:CESq_Sigma_Sigma_1_ekl}.
Or, consider a better way to show resampled $\sigma$ and $\sigma_1$ values. ****

Figure~\ref{fig:CESq_Sigma_Sigma_1_kle} shows 
$\sigma$ and $\sigma_1$ values from the CES model with ($kl$)$e$ nesting.

<<CESq_Sigma_Sigma_1_kle, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($kl$)$e$ nesting.">>=
cesResamplePlotSigmaSigma_1(energyType="Q", nest="(kl)e")
@

Figure~\ref{fig:CESq_Sigma_Sigma_1_lek} shows 
$\sigma$ and $\sigma_1$ values from the CES model with ($le$)$k$ nesting.

<<CESq_Sigma_Sigma_1_lek, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($le$)$k$ nesting.">>=
cesResamplePlotSigmaSigma_1(energyType="Q", nest="(le)k")
@

Figure~\ref{fig:CESq_Sigma_Sigma_1_ekl} shows 
$\sigma$ and $\sigma_1$ values from the CES model with ($ek$)$l$ nesting.

<<CESq_Sigma_Sigma_1_ekl, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelTernaryGraphHeight, fig.cap="CES (with energy) resample model $\\sigma$ and $\\sigma_1$ values, ($ek$)$l$ nesting.">>=
cesResamplePlotSigmaSigma_1(energyType="Q", nest="(ek)l")
@

@@

**** Replace Figure~\ref{fig:CES_GDP_Lattice_Graph} with four graphs that show
the range of predictions from resamples with each nesting. ****
